---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dfuzz

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/dfuzz)](https://CRAN.R-project.org/package=dfuzz)
<!-- badges: end -->

The goal of __{dfuzz}__ is to help you cleaning up a messy column of strings
of characters in your `tibble` or `data.frame`.

This package is __highly experimental__ and is not yet ready for being used for real applications.

It is build around two dependencies which themselves have no dependencies:

- [__{rlang}__](https://github.com/r-lib/rlang)

- [__{stringdist}__](https://github.com/markvanderloo/stringdist), and it is possible to use the full power of the function `stringdist()` from this excellent package.


__{dfuzz}__ aims at being compatible with both _tidyverse_ and _base_ R dialects.


## Installation

You can install this package using __{remotes}__ (or __{devtools}__):

```r
remotes::install_github("courtiol/dfuzz")
```

## Example

```{r example}
library(dfuzz)

## a toy example:
test_df <- data.frame(fruit = c("banana", "blueberry", "limon", "pinapple",
                                "aple", "apple", "ApplE", "bonana"))
test_df

## fast and dirty workflow:
clean_df1 <- fuzzy_tidy(test_df, fruit)
clean_df1

## more subtle workflow:
template_fruit <- fuzzy_match(test_df, fruit)
template_fruit
template_fruit$selected[1] <- "apple"
clean_df2 <- fuzzy_tidy(test_df, fruit, template_fruit)
clean_df2

## fast and dirty workflow with {tidyverse}:
library(tidyverse)
test_df %>%
  fuzzy_tidy(fruit) %>%
  mutate(fruit = fruit.tidy) %>%
  select(-contains("fruit."))

## more subtle workflow with {tidyverse}:
test_df %>%
  mutate(fruit = str_to_title(fruit)) %>%
  fuzzy_match(fruit) -> template_fruit
template_fruit

template_fruit %>%
  mutate(selected = fct_recode(selected, Apple = "Aple")) -> better_template_fruit

better_template_fruit

test_df %>%
  mutate(fruit = str_to_title(fruit)) %>%
  fuzzy_tidy(fruit, better_template_fruit) -> clean_df3
clean_df3

clean_df3 %>%
  mutate(fruit = fruit.tidy) %>%
  select(-contains("fruit."))
```

## Help \& feedbacks wanted!

If you find that this package is an idea worth pursuing, please let me know.
Developing is always more fun when it becomes a collaborative work.
So please also email me (or leave an issue) if you want to get involved!
